\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Hyperlink setup
\usepackage{xcolor}
\definecolor{primarycolor}{HTML}{2b2b2b}
\definecolor{linkcolor}{HTML}{0056b3}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor
}

\newcommand{\sectionnumber}[1]{\textbf{#1}}

\newcommand{\resumename}[1]{{\textls[150]{\fontsize{40pt}{40pt}\selectfont\textbf{#1}}}}
\newcommand{\jobtitle}[1]{{\fontsize{15.5pt}{15pt}\selectfont\textbf{#1}}}
\newcommand{\contactinfo}[1]{{\fontsize{12pt}{14pt}\selectfont\color{black!70}#1}}

\newcommand{\sectiontitle}[1]{\textbf{\uppercase\expandafter{\romannumeral-`\0#1}}}

\newcommand{\sectiondivider}[2][0.4]{%
    \noindent
    \vspace{3pt}
    \textcolor{black}{%
        \noindent
        \makebox[\linewidth]{\rule{#1\linewidth}{0.5pt}%
        \hspace{5pt} \textbf{\uppercase{#2}} \hspace{5pt}%
        \rule{#1\linewidth}{0.5pt}}%
    }
    \vspace{3pt}
}

% Entry header: dates | role | org
\newcommand{\cventry}[3]{%
    \noindent
    \begin{tabular*}{\linewidth}{@{}p{4cm} p{10cm} @{\extracolsep{\fill}} r@{}}
        \textbf{\small #1} & \textbf{#2} & {\color{primarycolor}\small #3}
    \end{tabular*}
    \vspace{-3pt}
}

\newcommand{\project}[3]{%
    \noindent
    \begin{tabular*}{\linewidth}{@{}p{5.5cm} p{10cm} @{\extracolsep{\fill}} r@{}}
        \textbf{#1} & {#2} & {\color{linkcolor}\small #3}
    \end{tabular*}
}
 
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.3em}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{14pt}

\pagenumbering{arabic}

\begin{document}

\begin{center}
    \resumename{Hadi Ademola S.} \\[0.5cm]
    \jobtitle{Frontend Engineer . Web Developer . Mobile Developer} \\[0.2cm]
    \contactinfo{
        \faPhone* \ +234 813 855 3465 \textbar\ 
        \faEnvelope \ \href{mailto:hadiademola@gmail.com}{hadiademola@gmail.com} \textbar\ 
        \faMapMarker* \ Abuja, Nigeria
    } \\[0.3cm]
    \contactinfo{
        \faGlobe \ \href{https://hadiademola.vercel.app}{hadiademola.com} \textbar\
        \faGithub \ \href{https://github.com/Hardeygold205}{github.com/Hardeygold205} \textbar\ 
        \faLinkedin \ \href{https://linkedin.com/in/Hardeygold205}{linkedin.com/in/Hardeygold205}
    }
\end{center}

\vspace{0.1cm}

\section{Personal Statement}
\setstretch{1.65}
Frontend and Mobile Engineer with hands-on experience designing, building, and shipping production-level applications across web and mobile platforms. I hold a B.Sc. in Physics from the University of Ibadan, which has sharpened my analytical thinking and systematic approach to problem-solving qualities I bring directly into software architecture and performance optimization.
I have worked on multiple production-level applications involving authentication systems, real-time features and API integrations. I enjoy taking ownership of features end-to-end and building systems that are reliable, maintainable, and designed for real users especially in environments with low bandwidth and device constraints.

\section{Education \& Certifications}
\vspace{-0.3cm}
\cventry{2021 -- 2025}{Bachelor of Science, Physics}{University of Ibadan, Nigeria}
\vspace{-0.5cm}
\begin{itemize}
    \item Graduated with a strong foundation in Computational Physics, Data Analysis, and Mathematical Methods in Physics.
    \item Final year project: "Geophysical Evaluation of Subsurface Layers for Structural Foundations using Electrical Resistivity"
\end{itemize}
 
\vspace{1pt}
\cventry{2023 -- 2024}{Software Engineering (Backend Track)}{ALX Africa}
\vspace{-0.5cm}
\begin{itemize}
    \item Intensive programme covering systems programming, backend development and data structures .
    \item Completed projects involving API development and performance optimization using languages like C, Python, and Node.js.
\end{itemize}
 
\vspace{1pt}
\cventry{2022 -- 2023}{Frontend Web Development}{FreeCodeCamp}
\vspace{-0.5cm}
\begin{itemize}
    \item Completed structured curriculum in responsive web design, JavaScript algorithms, and frontend frameworks.
    \item Built multiple projects including a personal portfolio, and a markdown previewer using HTML, CSS, JavaScript.
\end{itemize}

\vspace{1pt}
\cventry{2025 -- Present}{National Youth Service Corps (NYSC)}{Federal Republic of Nigeria}
\vspace{-0.5cm}
\begin{itemize}
    \item Currently serving in the NYSC program, contributing to community development and national service initiatives.
\end{itemize}

\section{Technical Skills}
\vspace{-0.3cm}
\begin{tabbing}
\hspace{6cm} \= \hspace{6cm} \= \kill
\textbf{\uppercase{Languages:}} \> HTML \textbar\ CSS \textbar\ JavaScript \textbar\ TypeScript \textbar\ Python \textbar\ LaTex \textbar\ NodeJs  \\
\> PHP (Basic) \textbar\ Solidity (Basic) \textbar\ C (Basic) \\[1ex]

\textbf{\uppercase{Frameworks/Libraries:}} \> React \textbar\ NextJs \textbar\ React Native \textbar\ React Native (Expo) \textbar\ Vue (Basic) \textbar\ Angular (Basic) \\
\> ExpressJS \textbar\ NestJs \textbar\ Laravel \textbar\ Django (Basic) \\[1ex]

\textbf{\uppercase{Database:}} \> MongoDB \textbar\ PostgreSQL \textbar\ SQL (Basic) \\[1ex]

\textbf{\uppercase{Tools:}} \> Firebase \textbar\ Supabase \textbar\ Moodle \textbar\ Git/Github \textbar\ Linux/Unix

\end{tabbing}

\vspace{0.1cm}

\section{Professional Experience}
\vspace{-0.3cm}
\cventry{Years}{Role}{Company}
\cventry{2025 -- Present}{Frontend/Mobile Developer (Intern)}{Extension Africa}
\vspace{-0.4cm}
\begin{itemize}
    \item Built and maintained mobile and web applications using React and React Native
    \item Improved performance and structure of an existing web platform through refactoring.
    \item Designed and implemented authentication flows, onboarding systems, and responsive UI components.
    \item Collaborated within a cross-functional team using modern development workflows.
\end{itemize}

\cventry{2025 -- 2026}{Mobile Developer}{Play2score}
\vspace{-0.4cm}
\begin{itemize}
    \item Building a mobile and web application using React Native and Expo for an organizatiom.
    \item Integrated Supase for user authentication, real-time data, and notifications.
    \item Designed onboarding, login/signup, forms and all UI with responsive layouts.
    \item Collaborated with a team of 3 using Git and GitHub, and other social platform.
\end{itemize}

\cventry{2024 -- 2025}{FullStack Developer (Personal Project)}{ExcelExchange}
\vspace{-0.4cm}
\begin{itemize}
    \item Developed a crypto trading app enabling users to swap cryptocurrencies for local fiat currencies.
    \item Designed and built responsive UI using React (web) and React Native (mobile).
    \item Displayed real-time crypto price data using APIs and charting libraries.
    \item Focused on user-friendly flows for wallet authentication, local transaction records, and conversion tracking.
\end{itemize}

\cventry{2024 -- 2025}{FullStack Developer (Personal Project)}{CoinBitExtension}
\vspace{-0.4cm}
\begin{itemize}
    \item Built a decentralized dApp extension focused on interacting with blockchain networks.
    \item Integrated wallet connect functionality for Ethereum and Solana using WalletConnect and Phantom.
    \item Designed responsive UI with React, TailwindCSS, and Next.js.
    \item Worked with smart contract interactions for on-chain transactions.
    \item Implemented backend with Node.js and MongoDB (in progress).
    \item Hosted MVP with Vercel and managed codebase via GitHub.
\end{itemize}

\cventry{2023 -- 2024}{Mobile Developer}{CampusRide}
\vspace{-0.4cm}
\begin{itemize}
    \item Built and deployed a mobile and web application using React Native and Expo for university-based transportation.
    \item Integrated Firebase for user authentication, real-time data, and notifications.
    \item Designed onboarding, login/signup, and driver-rider selection flows with responsive layouts.
    \item Collaborated with a team of 2 using Git and GitHub, and practiced agile methodologies.
\end{itemize}

\cventry{2025 -- 2026}{Frontend Engineer \& Project Lead}{Branovax Technology}
\vspace{-0.4cm}
\begin{itemize}
    \item Led a 3-member team to design and deploy custom web solutions for clients, utilizing NextJS with SEO Implemented.
    \item Owned end-to-end project delivery and developed scalable web applications tailored to client requirements.
    \item Implemented secure authentication, real-time data dashboards, and responsive UI/UX.
\end{itemize}

\newpage
\cventry{2023 -- 2024}{SIWES Intern}{Imaginarium Creative Global}
\vspace{-0.4cm}
\begin{itemize}
    \item Learned industry-level photography and editing workflows during a 6-week industrial training.
    \item Assisted in editing promotional media and handling client photography sessions.
    \item Developed a basic photo gallery portfolio site using HTML, CSS, and JavaScript.
\end{itemize}

\vspace{0.1cm}

\section{Projects}
\vspace{-0.3cm}
\noindent
\project{Project}{Stack}{Link}
\project{\large{Branovax Technology}}{ NextJS, TailwindCSS, Node.Js, PostgreSQl }{\contactinfo{ \href{https://branovax.com}{Live Dashboard}}} 
\project{\large{Extension Africa Academy}}{ NextJS, TailwindCSS, Moodle(PHP), Apache  }{\contactinfo{ \href{https://academy.extensionafrica.com}{Live Dashboard}}}
\project{\large{Excel Exchange}}{ Vite+React, React Native, TailwindCSS, Node.Js, MongoDB }{\contactinfo{ \href{https://excelexchange.vercel.app}{Live Dashboard}}}
\project{\large{Personal Portfolio Website}}{ NextJS, TypeScript, TailwindCSS, EmailJs }{\contactinfo{ \href{https://hadiademola.vercel.app}{Live Dashboard}}}
\project{\large{CoinBitz Extension}}{ Vite+React, TailwindCSS, ExpressJs, Web3.Js PostgreSQl }{\contactinfo{ \href{https://coinbit-extension.vercel.app}{Live Dashboard}}}
\project{\large{CampusRide App}}{ React Native, Expo Router, NativeWind, NodeJs, Docker }{\contactinfo{ \href{https://github.com/Hardeygold205/CampusRide}{Github Repository}}}
\project{\large{Twitter Gain App}}{ HTML, CSS, JavaScript, BootStrap }{\contactinfo{ \href{https://github.com/Hardeygold205/twitter-gain-app}{Github Repository}}}
\project{\large{JetSender}}{ NextJS, TypeScript, TailwindCSS, NodeMailer }{\contactinfo{ \href{https://github.com/Hardeygold205/BulkEMailSender}{Github Repository}}}
\project{\large{Telegram Notify Bot}}{ NodeJS, JavaScript, BotFather }{\contactinfo{ \href{https://github.com/Hardeygold205/NottifyBot}{Github Repository}}}


\section{Interest \& Other Activities}
\noindent
\textbf{Blockchain \& Web3:} Active interest in decentralised finance (DeFi), smart contract development with Solidity, and building user-friendly dApp interfaces. \\[0.4ex]
\textbf{Physics \& Computing:} Background in physics informs strong interest in computational thinking and graphical modeling. \\[0.4ex]
\textbf{Open Source:} Actively maintain personal repositories on GitHub; interested in contributing to open-source tools. \\[0.4ex]
\textbf{Community:} Interested in developer communities and knowledge sharing especially in the tech ecosystem.

\section{References}
\noindent
Available upon request.

\end{document}
